\batcave: Bayesian Analysis Tools for Context-Aware Variant Evaluation

### 2019-10-04 NAR_DRAFT.tex
commmit to merge

\section{Software Availability}

The \texttt{batcaver} R package can be downloaded or installed from \texttt{github.com/bmannakee/batcaver}
The version of \texttt{batcaver} used to generate results, and all analysis code have been preserved on Zenodo \texttt{https://doi.org/10.5281/zenodo.3471715}

@@

This work was supported by the National Science Foundation via Graduate Research Fellowship award number DGE-1143953 to BKM and by the National Institute of General Medical Sciences of the National Institutes of Health under award number R01GM127348 to RNG.
We thank Prof.\ Edward J. Bedrick for fruitful discussions about the statistical model.

@@

\begin{figure}[b]
  \begin{center}
  \includegraphics[width=\textwidth]{figures/fig_wgs.pdf}
  \end{center}
  \caption{Model performance on 100X simulated whole genome.
  \textbf{(A)} Precision recall curves and \textbf{(B)} Reciever operating characteristic curves for 3 mutation profiles.
  Distribution of estimated true positive probabilities for true positive  variants for \textbf{(C)} the MuTect model and \textbf{(D))} the \batcave model.
  A perfectly calibrated model would generate the diagonal line.}
\label{NAR-wgs_fig}
\end{figure}

\clearpage
\begin{figure}
  \begin{center}
  \includegraphics{figures/ppv_wgs.pdf}
  \end{center}
  \caption{Model performance on 100X simulated whole genome. 
  Precision vs. Recall for five different probability cutoffs. 
  Note the restricted axes to improve readability of points.}
\label{NAR-ppv_wgs_fig}
\end{figure}

>>>>

\section{Software Availability}
\bkmcomment{working on this today}

github for source code

zenodo for figures, simulations

zenodo for package at time of bioarxiv

@@

This work was supported by the National Science Foundation via Graduate Research Fellowship award number DGE-1143953 to BKM and by the National Institute of General Medical Sciences of the National Institutes of Health under award number R01GM127348 to RNG.
We thank Prof.\ Edward J. Bedrick for fruitful discussions about the statistical model.
\bkmcomment{Acknowledge HPC.}

@@

\begin{figure}[b]
  \begin{center}
  \includegraphics[width=\textwidth]{figures/fig_wgs.png}
  \end{center}
  \caption{Model performance on 100X simulated whole genome.
  \textbf{(A)} Precision recall curves and \textbf{(B)} Reciever operating characteristic curves for 3 mutation profiles.
  Distribution of estimated true positive probabilities for true positive  variants for \textbf{(C)} the MuTect model and \textbf{(D))} the \batcave model.
  A perfectly calibrated model would generate the diagonal line.}
\label{NAR-wgs_fig}
\end{figure}

\clearpage
\begin{figure}
  \begin{center}
  \includegraphics{figures/ppv_wgs.pdf}
  \end{center}
  \caption{Model performance on 100X simulated whole genome. 
  Positive predictive values vs. Recall for five different probability cutoffs. 
  Note the restricted axes to improve readability of points.}
\label{NAR-ppv_wgs_fig}
\end{figure}
